\documentclass[UTF8]{article}

\usepackage{geometry}

\special{papersize=2in,2in}%纸张大小为8.5inch×11inch

\usepackage{amsmath,amssymb}  % 数学字符与公式宏包，分数多用\dfrac方能显示我认可的大小
\usepackage{calc}
\usepackage{units} %单位宏包
\usepackage{graphicx}   % 插图必用宏包
\usepackage{enumerate}



% opening

\begin{document}


	\title{Journal club report}	
	\date{Oct 20, 2017} 
	\maketitle
The main contribution of this paper is:
\begin{enumerate}
	\item introduce tensor train decomposition and apply tensor rank to solve tensor completion.
	\item Introduce two algorithm based on TT rank.
	\item Introduce a new technique called KA to extend tensor dimension.
\end{enumerate}

Main discussion:
\begin{enumerate}
	\item  tensor train decomposition
	\begin{equation}
	\mathcal{A}_{[k]}=\text{reshape} (\mathcal{A}, \prod_{s=1}^k n_s,\prod_{s=k+1}^d n_s)
	\end{equation}
	The difference between tucker decomposition and tensor train decomposition is that tucker decomposition is just mode-$k$ matricization but tensor train decomposition is mode-$(1,2,…,k)$  matricization.
	\item how to prove the tensor train decomposition is balanced?
	In this paper, via von neuman entropy, we obtain that 
	\begin{equation}
	S=\text{log}_2 r_k
	\end{equation}
	Because the bigger the $S$, the stronger the correlation between subsystem $A$ and $B$.  $S$ is bounded by $r_k$ , $r_k$ is bounded by  $m=I_k$.
	It just prove that tucker decomposition is unbalanced. And  $r_k$ should be as large as possible. So tensor train decomposition can be a solution.
	\item Algorithm
	The two algorithms in this paper is easy to understand, the main difference is the step unfold the tensor $\mathcal{A}$  to get ${\bf{A}}_k$  (TT decomposition).
	TMac-TT is a good algorithm due to its multilinear matrix factorization model. 
	\item KA 
	Ket augmentation(KA) is a technique to represent a lower-order tensor by a high-order one. The expansion method here is hard to imagine how the elements in the new tensor are arranged.
	\item Balance
	Compared with tucker decomposition, the tensor train decompositin is more banlanced. 
	Due to
		\begin{equation}
	\mathcal{A}_{[k]}=\text{reshape} (\mathcal{A}, \prod_{s=1}^k n_s,\prod_{s=k+1}^d n_s)
	\end{equation}
	,
	to some extent,  $k$ is closer to $d/2$ ,  ${\bf{A}}_k$  is more balanced. 
	\item the possible future work\\
	  1.due to the balance problem, we think that block+multilinear low-rank which we didn’t finished last time is likely to succeed.\\
	  2.TMac algorithm in this paper perform better than others, maybe we can use other matrix factorization method to have a try. Or use it to other application.
\end{enumerate}


\end{document}